Title

### 2014-07-18 paper.tex
move 図s around
write write write - result: training data

% where we got the data
We used the review data sets of the Qt project collected by Hamasaki et al.
Only reviews in the master branch of \texttt{qtbase} project are considered,
as it is the most active branch.

@@

\begin{figure}
\centering
\includegraphics[width=2.5in]{hierarchy}
\caption{Relationship between documents.
Each rectangle represents a document, which may either be a commit message or a comment.}
\label{fig:hierarchy}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=2.5in]{preprocess}
\caption{The data preparation process.
Automatically generated texts are removed, remaining text is tokenized, stop words are removed, remaining tokens are stemmed,
and are converted into a vector.}
\label{fig:preprocess}
\end{figure}

@@

>>>>

% where we got the data
We used the review data sets of the Qt project collected by Hamasaki et al TODO(cite properly).
Only reviews in the master branch of \texttt{qtbase} project are considered,
as it is the most active branch.

@@

\begin{figure}[h]
\centering
\includegraphics[width=2.5in]{hierarchy}
\caption{Relationship between documents.
Each rectangle represents a document, which may either be a commit message or a comment.}
\label{fig:hierarchy}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=3in]{preprocess}
\caption{The data preparation process.
Automatically generated texts are removed, remaining text is tokenized, stop words are removed, remaining tokens are stemmed,
and are converted into a vector.}
\label{fig:preprocess}
\end{figure}

@@

After the 320 sample comments have been labeled,
they are scored based on the number of ``yes'' given to the sample.
The table below shows the distribution of scores for the training data.

\begin{center}
\begin{tabular}{|r|r|}
\hline
\bfseries Score & \bfseries Count \\
\hline
0 & 87 \\ 1 & 60 \\ 2 & 51 \\ 3 & 122 \\
\hline
\end{tabular}
\end{center}
